Applications of limited information strategies in Menger's game

### 2017-03-15 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
update applications of limited info menger with final revisions

\begin{definition}
  For any cardinal \(\kappa\), let \(\onePtLind\kappa=\kappa\cup\{\infty\}\) denote
  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
  sets containing it.
\end{definition}

@@

\begin{game}
  Let \(\schFillStrictGame\kappa\) denote
  \term{Scheepers' strict countable-finite union game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzcd}[arrows=Rightarrow]
  &
  \pl F \kmarkwin{k+1} \menGame{\onePtLind\kappa}
  \Leftrightarrow
  \pl F \kmarkwin{k+1} \schFillIntGame{\kappa}
    \arrow[d] \\
  \pl F \ktactwin{k+1} \schFillStrictGame{\kappa}
    \arrow[r] &
  \pl F \kmarkwin{k+1}\schFillGame{\kappa}
  \Leftrightarrow
  \pl F \kmarkwin{k+1} \schFillInitialGame{\kappa}
      \arrow[d] \\
  &
  \pl F \kmarkwin{k+1} \schFillStrictGame{\kappa}
\end{tikzcd}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  \(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\menGame{\onePtLind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\onePtLind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).

  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\onePtLind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\onePtLind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\onePtLind\kappa}\).

@@

  \(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\): Let \(\sigma\) be a winning
  \((k+1)\)-mark for \(\pl F\) in
  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let
  \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that \(C_n\) is covered when
  attacked by \(\<C_n,C_{n+1},\dots\>\) for all \(n<\omega\).

@@

  \(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-tactic for \(\pl F\) in
  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then for every valid attack \(\<C_0,C_1,C_2,\dots\>\) by \(\pl C\) in
  \(\schFillGame\kappa\), it follows that \(\<C_0,C_1+1,C_2+2,\dots\>\) is a
  valid attack by \(\pl C\) in \(\schFillStrictGame\kappa\) as
  \(C_{n+1}\supseteq C_n\) ensures that
  \(C_{n+1}+(n+1)\) includes all the \(n\) added elements in \(C_n+n\)
  in addition to at least one more.
  Thus \(\tau\) defined by
    \[
      \tau(\<C_n,\dots,C_{n+i}\>,n+i)
        =
      \sigma(\<C_n+n,\dots,C_{n+i}+(n+i)\>)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that
  \(\bigcup_{n<\omega}(C_n+n)\supseteq\bigcup_{n<\omega}C_n\)
  is covered when attacked by \(\<C_0,C_1+1,C_2+2,\dots\>\).

@@

\begin{figure}[ht]
\begin{tikzcd}[arrows=Rightarrow]
  \alcompS\kappa
    \arrow[r]
    \arrow[d] &
  \pl F \kmarkwin2 \menGame{\onePtLind\kappa}
  \Leftrightarrow
  \pl F \kmarkwin2 \schFillIntGame{\kappa}
    \arrow[d] \\
  \pl F \ktactwin2 \schFillStrictGame{\kappa}
    \arrow[r] &
  \pl F \kmarkwin2\schFillGame{\kappa}
  \Leftrightarrow
  \pl F \kmarkwin2 \schFillInitialGame{\kappa}
      \arrow[d] \\
  &
  \pl F \kmarkwin2 \schFillStrictGame{\kappa}
\end{tikzcd}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
\label{GamesDiagram2}
\end{figure}

@@

\begin{lemma}
  Let \(\sigma(\mc{U}, n)\) be a Markov strategy for \(F\) in
  \(\menGame{X}\), and \(\mc{O}\) collect all open covers of \(X\). Then the
  set
    \[
      R_n = \bigcap_{\mc{U}\in\mc{O}} \sigma(\mc{U},n)
    \]
  is relatively compact to \(X\). If \(\sigma\) is a winning
  Markov startegy, then \(\bigcup_{n<\omega} R_n = X\).
\end{lemma}

@@

\begin{proof}
  If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
  \(\sigma(n)=R_n\) is a winning \(0\)-mark, which of course gives a
  winning \(1\)-mark. The previous lemma finishes the proof.
\end{proof}

@@

\begin{proof}
  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
  and thus are nowhere dense in nonmeager \(\mathbb R\),
  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
  intervals with rational endpoints (with or without rationals removed)
  witnesses second-countability.

@@

\begin{proof}
  If \(S\supseteq\{s_n:n<\omega\}\) for distinct \(s_n\),
  then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering
  \(S\), showing that all relatively compact sets are finite, and \(R_\omega\)
  is not \(\sigma\)-relatively-compact. The set \(R_\omega\setminus\mathbb Q\)
  is open, but the closure of any open subset must contain a rational, so
  this space is not regular. Finally, the space is not second-countable,
  since for any countable collection of open sets \(\{U_n:n<\omega\}\),
  we may choose \(p_n\in U_n\)
  and note \(R_\omega\setminus\{p_n:n<\omega\}\) is an open set not containing
  any \(U_n\).

  Define the winning strategy \(\sigma\) for \(\pl F\) in
  \(\menGame{R_\omega}\) as follows: let
  \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
  where \(C_n\) witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
  and \(\mc U_{2n}\),
  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
\end{proof}

>>>>

\begin{definition}
  For any cardinal \(\kappa\), let \(\onePtLind\kappa=\kappa\cup\{\infty\}\) denote
  the \term{one-point Lindel\"ofication} of discrete \(\kappa\), where points in
  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
  sets containing it.
\end{definition}

@@

\begin{game}
  Let \(\schFillStrictGame\kappa\) denote
  \term{Scheepers' strict countable-finite union game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supsetneq C_n\),
  followed by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzcd}[arrows=Rightarrow]
  &
  \pl F \kmarkwin{(k+1)} \menGame{\onePtLind\kappa}
    \arrow[d]
    \arrow[r,Leftrightarrow]
  &
  \pl F \kmarkwin{(k+1)} \schFillIntGame{\kappa}
      \arrow[d]  \\
  \pl F \ktactwin{(k+1)} \schFillStrictGame{\kappa}
    \arrow[r] &
  \pl F \kmarkwin{(k+1)}\schFillGame{\kappa}
      \arrow[d]
      \arrow[r,Leftrightarrow]
  &
  \pl F \kmarkwin{(k+1)} \schFillInitialGame{\kappa}
    \arrow[ld]\\
  &
  \pl F \kmarkwin{(k+1)} \schFillStrictGame{\kappa}
\end{tikzcd}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  \(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\menGame{\onePtLind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\onePtLind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  where \(|s|\leq k\)
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).

  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\):
  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\onePtLind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\onePtLind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U\>),n)
    \]
  where \(|s|\leq k\)
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\onePtLind\kappa}\).

@@

  \(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\): Let \(\sigma\) be a winning
  \((k+1)\)-mark for \(\pl F\) in
  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let
  \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  where \(|s|\leq k\)
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that \(C_n\) is covered when
  attacked by \(\<C_n,C_{n+1},\dots\>\) for all \(n<\omega\).

@@

  \(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\):
  Let \(\sigma\) be a winning \((k+1)\)-tactic for \(\pl F\) in
  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then for every valid attack \(\<C_0,C_1,C_2,\dots\>\) by \(\pl C\) in
  \(\schFillGame\kappa\), it follows that \(\<C_0,C_1+1,C_2+2,\dots\>\) is a
  valid attack by \(\pl C\) in \(\schFillStrictGame\kappa\) as
  \(C_{n+1}\supseteq C_n\) ensures that
  \(C_{n+1}+(n+1)\) includes all the \(n\) added elements in \(C_n+n\)
  in addition to at least one more.
  Thus \(\tau\) defined by
    \[
      \tau(\<C_n,\dots,C_{n+i}\>,n+i)
        =
      \sigma(\<C_n+n,\dots,C_{n+i}+(n+i)\>)
    \]
  where \(i\leq k\)
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
  considering that \(\sigma\) ensures that
  \(\bigcup_{n<\omega}(C_n+n)\supseteq\bigcup_{n<\omega}C_n\)
  is covered when attacked by \(\<C_0,C_1+1,C_2+2,\dots\>\).

@@

\begin{figure}[ht]
\begin{tikzcd}[arrows=Rightarrow]
  \alcompS\kappa
    \arrow[r]
    \arrow[d] &
      \pl F \kmarkwin{(k+1)} \menGame{\onePtLind\kappa}
        \arrow[d]
        \arrow[r,Leftrightarrow]
      &
      \pl F \kmarkwin{(k+1)} \schFillIntGame{\kappa}
          \arrow[d]  \\
      \pl F \ktactwin{(k+1)} \schFillStrictGame{\kappa}
        \arrow[r] &
      \pl F \kmarkwin{(k+1)}\schFillGame{\kappa}
          \arrow[d]
          \arrow[r,Leftrightarrow]
      &
      \pl F \kmarkwin{(k+1)} \schFillInitialGame{\kappa}
        \arrow[ld]\\
      &
      \pl F \kmarkwin{(k+1)} \schFillStrictGame{\kappa}
\end{tikzcd}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
\label{GamesDiagram2}
\end{figure}

@@

\begin{lemma}
  Let \(\sigma\) be a Markov strategy for \(\pl F\) in
  \(\menGame{X}\), and \(\mc{O}\) collect all open covers of \(X\). Then the
  set
    \[
      R_n = \bigcap_{\mc{U}\in\mc{O}} \sigma(\mc{U},n)
    \]
  is relatively compact to \(X\). If \(\sigma\) is a winning
  Markov startegy, then \(\bigcup_{n<\omega} R_n = X\).
\end{lemma}

@@

\begin{proof}
  If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
  \(\sigma(n)=R_n\) defines a winning \(0\)-mark \(\sigma\),
  which of course gives a
  winning \(1\)-mark. The previous lemma finishes the proof.
\end{proof}

@@

\begin{proof}
  Note that \(\pi\) is a point that cannot be separated from the closed
  set \(\mathbb Q\) by open sets, demonstrating non-regularity.
  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
  and thus are nowhere dense in nonmeager \(\mathbb R\),
  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
  intervals with rational endpoints (with or without rationals removed)
  witnesses second-countability.

@@

\begin{proof}
  If \(S\supseteq\{s_n:n<\omega\}\) for distinct \(s_n\),
  then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering
  \(S\), showing that all relatively compact sets are finite, and \(R_\omega\)
  is not \(\sigma\)-relatively-compact. The set \(R_\omega\setminus\mathbb Q\)
  is open, but the closure of any open subset must contain a rational, so
  this space is not regular. Finally, the space is not second-countable,
  since for any countable collection of nonempty
  open sets \(\{U_n:n<\omega\}\), we may choose \(p_n\in U_n\)
  and note \(R_\omega\setminus\{p_n:n<\omega\}\) is an open set not containing
  any \(U_n\).

  Define the winning strategy \(\sigma\) for \(\pl F\) in
  \(\menGame{R_\omega}\) as follows: let
  \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
  where \(C_n=\{c_{i,n}:i<\omega\}\)
  witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
  and \(\mc U_{2n}\),
  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
\end{proof}
